---
title: "Recommended_system_shopalyst"
author: "Ganeshna sri teja saikiran"
date: "31 January 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading data
```{r}
library(data.table)
library(reshape2)

shopperlyst_rec = read.csv(file.choose())
colnames(shopperlyst_rec) = c("TimeStamp", "Event", "Product_Id", "Shopper_Id", "department", "category", "sub_category", "gender", "brand")
set.seed(111)

```


#2 Identify the top 5 products (from the event log) that could be recommended to the below customers:

```{r}
library(recommenderlab)
library(reshape2)

product = acast(shopperlyst_rec[c(1:10000) , c("Shopper_Id", "Product_Id")],
                      Shopper_Id ~ Product_Id,length)

product = as(product, "realRatingMatrix")

product_shop = binarize(product, minRating = 1)

rec = Recommender(product_shop[1:nrow(product_shop)],method="UBCF")

product_item = function(customer_key) {
  
  cust_products = product[customer_key,]
  product_sshop = as(as(cust_products, "matrix"), "binaryRatingMatrix")

  recom = predict(rec, product_sshop,n=5)
  
  return(as(recom,"list"))
}

product_item("4590FBB2C98F98BF51769EB162F527D9")
product_item("135BC3FBD2C32B6F2DC6BAA92EA63747")
product_item("DCF1C2CD4351DF74551E7AE3A5365983")





